Pteropod biomarker analysis

### 2018-03-02 index.Rmd
Fixed plotly, corrected axis labels

  dat <- prd_vl()[, 1] %>% 
    as.matrix

  scene <- list(
    aspectmode = 'manual', 
    aspectratio = list(x = 0.5, y = 1, z = 0.3)
  )

  p <- plot_ly(z = ~dat) %>% add_surface() %>% 
    layout(scene = scene)
  p

>>>>

  dat <- prd_vl() %>% 
    spread_(key_col = names(.)[2], value_col = names(.)[1]) %>% 
    .[,-1] %>% 
    as.matrix

  scene <- list(
    aspectmode = 'manual', 
    aspectratio = list(x = 1, y = 1, z = 0.5), 
    xaxis = list(title = names(prd_vl()[3])),
    yaxis = list(title = names(prd_vl()[2])),
    zaxis = list(title = names(prd_vl()[1]))
    )

  p <- plot_ly(z = ~dat) %>% add_surface(colors = rev(RColorBrewer::brewer.pal(11, 'Spectral'))) %>% 
    layout(scene = scene)
  p
